prolfqua - An R-package for Analysing Proteomics Label Free Quantification Experiments

### 2022-04-01 inst/MyArticle/paper.Rmd
added GSEA reference

Label-Free Quantification (LFQ) Proteomics Experiments enable monitoring relative abundances of thousands of proteins in biological samples. For most studies, parallel group designs are used, e.g., treatment versus control are used [@de2022apoe2, @laubscher2021baf]. More recently, more complex experimental designs are implemented with increasing numbers of samples, i.e., factorial designs and longitudinal studies (time series), sometimes with repeated measurements on the same subject [@tan2022proteomic, @meier2021reduced]. The obtained data can be modeled using linear fixed-, mixed-, or random-effects models [@Bates2015FittingJSS]. Based on these models, tests can be applied to examine whether a factor or interactions are significant, or differences between factor levels can be estimated, and their significance tested. Proteins can be ordered or grouped using the estimated fold-change, $t$-statistics, scaled $p$-value, or false discovery rate (FDR) and then subjected to gene set enrichment or over-representation analysis [TODO ...] or validation experiments.

>>>>

Label-Free Quantification (LFQ) Proteomics Experiments enable monitoring relative abundances of thousands of proteins in biological samples. For most studies, parallel group designs are used, e.g., treatment versus control are used [@de2022apoe2, @laubscher2021baf]. More recently, more complex experimental designs are implemented with increasing numbers of samples, i.e., factorial designs and longitudinal studies (time series), sometimes with repeated measurements on the same subject [@tan2022proteomic, @meier2021reduced]. The obtained data can be modeled using linear fixed-, mixed-, or random-effects models [@Bates2015FittingJSS]. Based on these models, tests can be applied to examine whether a factor or interactions are significant, or differences between factor levels can be estimated, and their significance tested. Proteins can be ordered or grouped using the estimated fold-change, $t$-statistics, scaled $p$-value, or false discovery rate (FDR) and then subjected to gene set enrichment or over-representation analysis [@subramanian2005gene] or validation experiments.
